systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2005-11-02 paper/trunk/systemfit_other.tex
small last changes
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@580 591db2bd-e0a0-4d22-8c19-2192dbb7da31
added hausman citation
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@581 591db2bd-e0a0-4d22-8c19-2192dbb7da31

%    \item{probdfsys}{use the degrees of freedom of the whole system
%       (in place of the degrees of freedom of the single equation)
%       to calculate prob values for the t-test of individual parameters.}

@@

% Since the models that are fit using the \pkg{systemfit} package are
% typically random effects models, the effects may be inconsistent
% between the introduced variables and the regressors.

% results2sls  result of a 2SLS (limited information) estimation returned by systemfit. 
% results3sls  result of a 3SLS (full information) estimation returned by systemfit.

@@

As linear systems of equations can be estimated using
\code{systemfit}, nonlinear systems of equations can be estimated
using a similar function \code{nlsystemfit}. The usage for the
nonlinear estimation function is similar to \code{systemfit} and can
estimate system of equations using OLS, SUR, 2SLS and 3SLS methods.

@@

>>>>

@@

@@

As linear systems of equations can be estimated using
\code{systemfit}, nonlinear systems of equations \citep{hausman-1975}
can be estimated using a similar function \code{nlsystemfit}. The
usage for the nonlinear estimation function is similar to
\code{systemfit} and can estimate system of equations using OLS, SUR,
2SLS and 3SLS methods.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% left over from the older docs
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
